Relevance-based Quantization of Scattering Features for Unsupervised Mining of Environmental Audio

### 2018-06-28 paper/revision/responseToReviewers.tex

\item \emph{The dataset is too quickly described. I had to read ref\#36 to understand how it was built and made of. It would be nice to have an example of a labelled recording either as a spectrogram or scalogram to estimate the complexity of the scenes recorded. The event classes should also be detailed.}

$\rightarrow$ VL

\item \emph{It is a pity that the methods are not directly compared with the different strategies reported in ref\#36.}

$\rightarrow$
Since the tasks are different, it is not straightforward to compare the proposed methods with the approaches of ref\#36. In the former, we propose a method for acoustic scene similarity retrieval, while the latter discusses the problem of scene classification. In similarity retrieval, we would like to find other recordings in the dataset that are as similar to the original as possible (which here is defined as being in the same class). In scene classification, the task is to assign a class to each recording. In this sense, similarity retrieval is a more general problem. For our experiments, we calculate the p@k curves for each propsed method, allowing us to analyze the distribution of recordings most similar to a particular query recording. The classification setting is reproduced for $k = 1$, with the p@1 measure corresponding to the leave-one-out classification accuracy of nearest neighbors. As such, the classification task is a special case of the similarity retrieval setting considered here. We have modified the manuscript to make this distinction more clear.

@@

\item \emph{.P11L37: the comments about figure 3 (and others) is rather quick with no try of quantification of the differences/similarities between the p@k curves.}

$\rightarrow$ JA

\item \emph{.P12L37: Delete the comment addressed to one of the authors}

$\rightarrow$
This has been fixed in the revised manuscript.

@@

\item \emph{It would be interesting to see the contribution to the results of the Gammatone wavelet in comparison to Morlet or another more classical wavelet.}

$\rightarrow$ VL

\item \emph{There are several parameters that must be set in the experimentation. The reader may want to know if there is any specific parameter that is critical. What about M?}

$\rightarrow$ ML - Experiment with variable number $M$ for best approach.

@@

\item \emph{I do not see the authors have mentioned in Section 7 the following observation (Fig.3): for MFCC the relevance-based quantization improves the performance wrt BOF.}

$\rightarrow$ JA

\item \emph{Pag. 2, line 48: what "this" refers to?}

$\rightarrow$
This has been clarified in the revised manuscript.

@@

\item \emph{Pag. 2, line 49: "More closely matches... than...}

$\rightarrow$
This has been clarified in the revised manuscript.

\item \emph{Pag. 3, line 22: an cluster -\textgreater{} a cluster}

$\rightarrow$
This has been clarified in the revised manuscript.

@@

\item \emph{Pag. 3, line 23: Unconsistent sentence "These clusters to define..."}

$\rightarrow$
This has been clarified in the revised manuscript.

\item \emph{Equation (5): Notation is different from previous equations}

$\rightarrow$
The notation has been fixed for consistency with the other equations.

### 2018-06-28 paper/lostanlenRelevanceScattering.tex
Address some simple comments by R1
Address relation to DCASE 2013 systems

The experiments in this paper are carried out on the DCASE 2013 dataset \cite{7100934}.
This dataset consists of two parts, a public and a private subset, each made up of $100$ acoustic scene recordings sampled at $44100\,\mathrm{Hz}$ and $30$ seconds in duration. The dataset is evenly divided into $10$ acoustic scene classes. The recordings were made by three different recordists at a wide variety of locations in the Greater London area over a period of several months. No
systematic variations in the recordings covaried with scene
type: all recordings were made under moderate weather conditions, at varying times of day and week, and each recordist recorded each scene type. As a result, the dataset enjoys significant intra-class diversity while remaining of manageable size, making it suitable for evaluation of algorithmic design choices \cite{lagrange:hal-01082501}.

@@

With $p@5$ as our metric (cf. \cite{aucouturier2007bag} and \cite{lagrange:hal-01082501}), we see that replacing MFCCs by the logarithmically compressed scattering transform increases performance from $0.31$ to $0.49$. In addition, the relevance-based quantization using the closest similarity (\emph{RbQ-c}) further improves the performance to $0.54$ for a global increase of $0.23$. \vl{It is worth reminding what the baselines are.}

@@

\section*{Availability of data and materials}
The dataset supporting the conclusions of this article is available in the dcase2013 repository,  \sloppy \url{http://c4dm.eecs.qmul.ac.uk/sceneseventschallenge/description.html}.
The software supporting the conclusions of this article is available in
\begin{itemize}
\item Project name: article2017EstimationAmbiance
\item \sloppy Project home page: \url{https://github.com/mathieulagrange/paperRelevanceBasedSimilarity}
\item Programming language: Matlab
\item License: GNU GPL
\item Any restrictions to use by non-academics: license needed
\end{itemize}

>>>>

The experiments in this paper are carried out on the DCASE 2013 dataset \cite{7100934}.
Although the dataset was constructed for the task of acoustic scene classification, where the goal is to correctly assign the class of a given recording, we can use the same recordings and class labels for the task of acoustic scene similarity retrieval.
The dataset consists of two parts, a public and a private subset, each made up of $100$ acoustic scene recordings sampled at $44100\,\mathrm{Hz}$ and $30$ seconds in duration. The dataset is evenly divided into $10$ acoustic scene classes. The recordings were made by three different recordists at a wide variety of locations in the Greater London area over a period of several months. No
systematic variations in the recordings covaried with scene
type: all recordings were made under moderate weather conditions, at varying times of day and week, and each recordist recorded each scene type. As a result, the dataset enjoys significant intra-class diversity while remaining of manageable size, making it suitable for evaluation of algorithmic design choices \cite{lagrange:hal-01082501}.

@@

With $p@5$ as our metric (cf. \cite{aucouturier2007bag} and \cite{lagrange:hal-01082501}), we see that replacing MFCCs by the logarithmically compressed scattering transform increases performance from $0.31$ to $0.49$. In addition, the relevance-based quantization using the closest similarity (\emph{RbQ-c}) further improves the performance to $0.54$ for a global increase of $0.23$.

@@

\section*{Availability of data and materials}
The dataset supporting the conclusions of this article is available in the dcase2013 repository,  \sloppy \url{http://c4dm.eecs.qmul.ac.uk/sceneseventschallenge/description.html}.
The software supporting the conclusions of this article is available in
\begin{itemize}
\item \sloppy Project home page: \url{https://github.com/mathieulagrange/paperRelevanceBasedSimilarity}
\item Programming language: Matlab
\item License: GNU GPL
\item Any restrictions to use by non-academics: license needed
\end{itemize}
